% ADS_STATS first_author_count=12 total_count=90 h_index=32
\subsubsection*{First-Author}
\begin{itemize}
\item \textbf{2025:} Learning the Universe: cosmological and astrophysical parameter inference with galaxy luminosity functions and colours. \textit{\textbf{Christopher C. Lovell}, Tjitske Starkenburg, Matthew Ho \& others}, Monthly Notices of the Royal Astronomical Society 544 3949. \href{https://arxiv.org/abs/2411.13960}{arXiv:2411.13960}
\item \textbf{2025:} Synthesizer: a Software Package for Synthetic Astronomical Observables. \textit{\textbf{Christopher C. Lovell}, William J. Roper, Aswin P. Vijayan \& others}, The Open Journal of Astrophysics 8 152. \href{https://arxiv.org/abs/2508.03888}{arXiv:2508.03888}
\item \textbf{2023:} First light and reionisation epoch simulations (FLARES) - VIII. The emergence of passive galaxies at z $\geq$ 5. \textit{\textbf{Christopher C. Lovell}, Will Roper, Aswin P. Vijayan \& others}, Monthly Notices of the Royal Astronomical Society 525 5520. \href{https://arxiv.org/abs/2211.07540}{arXiv:2211.07540}
\item \textbf{2023:} A Hierarchy of Normalizing Flows for Modelling the Galaxy-Halo Relationship. \textit{\textbf{Christopher C. Lovell}, Sultan Hassan, Francisco Villaescusa-Navarro \& others}, Machine Learning for Astrophysics 21. \href{https://arxiv.org/abs/2307.06967}{arXiv:2307.06967}
\item \textbf{2023:} Extreme value statistics of the halo and stellar mass distributions at high redshift: are JWST results in tension with $\Lambda$CDM?. \textit{\textbf{Christopher C. Lovell}, Ian Harrison, Yuichi Harikane \& others}, Monthly Notices of the Royal Astronomical Society 518 2511. \href{https://arxiv.org/abs/2208.10479}{arXiv:2208.10479}
\item \textbf{2022:} An orientation bias in observations of submillimetre galaxies. \textit{\textbf{C. C. Lovell}, J. E. Geach, R. Davé \& others}, Monthly Notices of the Royal Astronomical Society 515 3644. \href{https://arxiv.org/abs/2106.11588}{arXiv:2106.11588}
\item \textbf{2022:} A machine learning approach to mapping baryons on to dark matter haloes using the EAGLE and C-EAGLE simulations. \textit{\textbf{Christopher C. Lovell}, Stephen M. Wilkins, Peter A. Thomas \& others}, Monthly Notices of the Royal Astronomical Society 509 5046. \href{https://arxiv.org/abs/2106.04980}{arXiv:2106.04980}
\item \textbf{2021:} Reproducing submillimetre galaxy number counts with cosmological hydrodynamic simulations. \textit{\textbf{Christopher C. Lovell}, James E. Geach, Romeel Davé \& others}, Monthly Notices of the Royal Astronomical Society 502 772. \href{https://arxiv.org/abs/2006.15156}{arXiv:2006.15156}
\item \textbf{2021:} SENGI: A small, fast, interactive viewer for spectral outputs from stellar population synthesis models. \textit{\textbf{C. C. Lovell}}, Astronomy and Computing 34 100444. \href{https://arxiv.org/abs/1911.12713}{arXiv:1911.12713}
\item \textbf{2021:} First Light And Reionization Epoch Simulations (FLARES) - I. Environmental dependence of high-redshift galaxy evolution. \textit{\textbf{Christopher C. Lovell}, Aswin P. Vijayan, Peter A. Thomas \& others}, Monthly Notices of the Royal Astronomical Society 500 2127. \href{https://arxiv.org/abs/2004.07283}{arXiv:2004.07283}
\item \textbf{2019:} Learning the relationship between galaxies spectra and their star formation histories using convolutional neural networks and cosmological simulations. \textit{\textbf{Christopher C. Lovell}, Viviana Acquaviva, Peter A. Thomas \& others}, Monthly Notices of the Royal Astronomical Society 490 5503. \href{https://arxiv.org/abs/1903.10457}{arXiv:1903.10457}
\item \textbf{2018:} Characterising and identifying galaxy protoclusters. \textit{\textbf{Christopher C. Lovell}, Peter A. Thomas, Stephen M. Wilkins}, Monthly Notices of the Royal Astronomical Society 474 4612. \href{https://arxiv.org/abs/1710.02148}{arXiv:1710.02148}
\end{itemize}

\subsubsection*{Second-Author}
\begin{itemize}
\item \textbf{2026:} Cloudy-Maraston: integrating nebular continuum and line emission with the Maraston stellar population synthesis models. \textit{Sophie L. Newman, \textbf{Christopher C. Lovell}, Claudia Maraston \& others}, Monthly Notices of the Royal Astronomical Society 545 staf1866. \href{https://arxiv.org/abs/2501.03133}{arXiv:2501.03133}
\item \textbf{2025:} Galactification: painting galaxies onto dark matter only simulations using a transformer-based model. \textit{Shivam Pandey, \textbf{Christopher C. Lovell}, Chirag Modi \& others}, Accepted in Science. \href{https://arxiv.org/abs/2511.08438}{arXiv:2511.08438}
\item \textbf{2025:} Synthesizer: Synthetic Observables For Modern Astronomy. \textit{Will J. Roper, \textbf{Christopher Lovell}, Aswin Vijayan \& others}. \href{https://arxiv.org/abs/2506.15811}{arXiv:2506.15811}
\item \textbf{2024:} First Light and Reionization Epoch Simulations (FLARES) - XIV. The Balmer/4000 Å breaks of distant galaxies. \textit{Stephen M. Wilkins, \textbf{Christopher C. Lovell}, Dimitrios Irodotou \& others}, Monthly Notices of the Royal Astronomical Society 527 7965. \href{https://arxiv.org/abs/2305.18175}{arXiv:2305.18175}
\item \textbf{2023:} First light and reionization epoch simulations (FLARES) IX: the physical mechanisms driving compact galaxy formation and evolution. \textit{William J. Roper, \textbf{Christopher C. Lovell}, Aswin P. Vijayan \& others}, Monthly Notices of the Royal Astronomical Society 526 6128. \href{https://arxiv.org/abs/2301.05228}{arXiv:2301.05228}
\item \textbf{2023:} JWST Constraints on the UV Luminosity Density at Cosmic Dawn: Implications for 21 cm Cosmology. \textit{Sultan Hassan, \textbf{Christopher C. Lovell}, Piero Madau \& others}, The Astrophysical Journal 958 L3. \href{https://arxiv.org/abs/2305.02703}{arXiv:2305.02703}
\item \textbf{2023:} First light and reionization epoch simulations (FLARES) X: environmental galaxy bias and survey variance at high redshift. \textit{Peter A. Thomas, \textbf{Christopher C. Lovell}, Maxwell G. A. Maltz \& others}, Monthly Notices of the Royal Astronomical Society 524 43. \href{https://arxiv.org/abs/2301.09510}{arXiv:2301.09510}
\item \textbf{2023:} First light and reionization epoch simulations (FLARES) XI: [O III] emitting galaxies at 5 $<$ z $<$ 10. \textit{Stephen M. Wilkins, \textbf{Christopher C. Lovell}, Aswin P. Vijayan \& others}, Monthly Notices of the Royal Astronomical Society 522 4014. \href{https://arxiv.org/abs/2301.13038}{arXiv:2301.13038}
\item \textbf{2022:} First Light And Reionisation Epoch Simulations (FLARES) - IV. The size evolution of galaxies at z $\geq$ 5. \textit{William J. Roper, \textbf{Christopher C. Lovell}, Aswin P. Vijayan \& others}, Monthly Notices of the Royal Astronomical Society 514 1921. \href{https://arxiv.org/abs/2203.12627}{arXiv:2203.12627}
\item \textbf{2021:} First Light And Reionization Epoch Simulations (FLARES) - II: The photometric properties of high-redshift galaxies. \textit{Aswin P. Vijayan, \textbf{Christopher C. Lovell}, Stephen M. Wilkins \& others}, Monthly Notices of the Royal Astronomical Society 501 3289. \href{https://arxiv.org/abs/2008.06057}{arXiv:2008.06057}
\item \textbf{2020:} Debunking Generalization Error or: How I Learned to Stop Worrying and Love My Training Set. \textit{Viviana Acquaviva, \textbf{Chistopher Lovell}, Emille Ishida}, Accepted in Science. \href{https://arxiv.org/abs/2012.00066}{arXiv:2012.00066}
\item \textbf{2020:} Nebular-line emission during the Epoch of Reionization. \textit{Stephen M. Wilkins, \textbf{Christopher C. Lovell}, Ciaran Fairhurst \& others}, Monthly Notices of the Royal Astronomical Society 493 6079. \href{https://arxiv.org/abs/1904.07504}{arXiv:1904.07504}
\item \textbf{2019:} Recalibrating the cosmic star formation history. \textit{Stephen M. Wilkins, \textbf{Christopher C. Lovell}, Elizabeth R. Stanway}, Monthly Notices of the Royal Astronomical Society 490 5359. \href{https://arxiv.org/abs/1910.05220}{arXiv:1910.05220}
\end{itemize}

\subsubsection*{Co-Authored}
\begin{itemize}
\item \textbf{2026:} The Nature of High-Redshift Massive Quiescent Galaxies - Searching for RUBIES-UDS-QG-z7 in FLARES. \textit{Jack C. Turner, Will J. Roper \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society. \href{https://arxiv.org/abs/2509.16111}{arXiv:2509.16111}
\item \textbf{2026:} CAMELS Environments: The Impact of Local Neighbours on Galaxy Evolution across the SIMBA, IllustrisTNG, ASTRID, and Swift-EAGLE Simulations. \textit{Xavier Sims, Daniel Anglés-Alcázar \& others including Christopher C. Lovell}. \href{https://arxiv.org/abs/2601.06290}{arXiv:2601.06290}
\item \textbf{2026:} Cosmological back-reaction of baryons on dark matter in the CAMELS simulations. \textit{Matthew Gebhardt, Daniel Anglés-Alcázar \& others including Christopher C. Lovell}. \href{https://arxiv.org/abs/2601.06258}{arXiv:2601.06258}
\item \textbf{2025:} ALMA Reveals Diverse Dust-to-gas Mass Ratios and Quenching Modes in Old Quiescent Galaxies. \textit{G. Lorenzon, D. Donevski \& others including Christopher C. Lovell}, The Astrophysical Journal 995 L63. \href{https://arxiv.org/abs/2509.10079}{arXiv:2509.10079}
\item \textbf{2025:} A new constraint on the $y$-distortion with FIRAS: implications for feedback models in galaxy formation and cosmic shear measurements. \textit{Giulio Fabbian, Federico Bianchini \& others including Christopher C. Lovell}, Submitted to Physical Review Letters. \href{https://arxiv.org/abs/2512.03038}{arXiv:2512.03038}
\item \textbf{2025:} Euclid: The first statistical census of dusty and massive objects in the ERO/Perseus field. \textit{G. Girardi, A. Grazian \& others including Christopher C. Lovell}, Accepted for publication in A\&A. \href{https://arxiv.org/abs/2512.01489}{arXiv:2512.01489}
\item \textbf{2025:} How Does Feedback Affect the Star Formation Histories of Galaxies?. \textit{Kartheik G. Iyer, Tjitske K. Starkenburg \& others including Christopher C. Lovell}, The Astrophysical Journal 994 174. \href{https://arxiv.org/abs/2508.21152}{arXiv:2508.21152}
\item \textbf{2025:} First Light And Reionisation Epoch Simulations (FLARES) XX: Comparing semi-analytic models at high-redshift. \textit{Louise T. C. Seeyave, Carlton M. Baugh \& others including Christopher C. Lovell}, Submitted to MNRAS. \href{https://arxiv.org/abs/2511.11982}{arXiv:2511.11982}
\item \textbf{2025:} Euclid Quick Data Release (Q1): Identification of massive galaxy candidates at the end of the Epoch of Reionisation. \textit{Euclid Collaboration, R. Navarro-Carrera \& others including Christopher C. Lovell}, Submitted to A\&A. \href{https://arxiv.org/abs/2511.11943}{arXiv:2511.11943}
\item \textbf{2025:} Think inside the box: cosmic variance and large-scale conformity of high-redshift massive galaxies in the FLAMINGO simulations. \textit{Seunghwan Lim, Sandro Tacchella \& others including Christopher C. Lovell}, Submitted to MNRAS. \href{https://arxiv.org/abs/2511.09618}{arXiv:2511.09618}
\item \textbf{2025:} First light and reionization epoch simulations (FLARES) $-$ XIX. Supermassive black hole mergers in the early Universe and their environmental dependence. \textit{Shihong Liao, Dimitrios Irodotou \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 543 3055. \href{https://arxiv.org/abs/2505.12591}{arXiv:2505.12591}
\item \textbf{2025:} Predicting the Subhalo Mass Functions in Simulations from Galaxy Images. \textit{Andreas Filipp, Tri Nguyen \& others including Christopher C. Lovell}, Published as a workshop paper at the ML4Astro Workshop at ICML 2025. \href{https://arxiv.org/abs/2510.14766}{arXiv:2510.14766}
\item \textbf{2025:} Behind the spotlight: a systematic assessment of outshining using NIRCam medium bands in the JADES Origins Field. \textit{Thomas Harvey, Christopher J. Conselice \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 542 2998. \href{https://arxiv.org/abs/2504.05244}{arXiv:2504.05244}
\item \textbf{2025:} Impact of stochastic star-formation histories and dust on selecting quiescent galaxies with JWST photometry. \textit{K. Lisiecki, D. Donevski \& others including Christopher C. Lovell}. \href{https://arxiv.org/abs/2509.10117}{arXiv:2509.10117}
\item \textbf{2025:} Learning the Universe: Physically Motivated Priors for Dust Attenuation Curves. \textit{L. Sommovigo, R. K. Cochrane \& others including Christopher C. Lovell}, The Astrophysical Journal 990 114. \href{https://arxiv.org/abs/2502.13240}{arXiv:2502.13240}
\item \textbf{2025:} Probing the co-evolution of Supermassive Black Holes and their hosts from scaling relations pairwise residuals: dominance of stellar velocity dispersion and host halo mass. \textit{Francesco Shankar, Mariangela Bernardi \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 541 2070. \href{https://arxiv.org/abs/2505.02920}{arXiv:2505.02920}
\item \textbf{2025:} Interpreting nebular emission lines in the high-redshift Universe. \textit{Aswin P. Vijayan, Robert M. Yates, \textbf{Christopher C. Lovell} \& others}, Published in the Open Journal of Astrophysics. \href{https://arxiv.org/abs/2507.20190}{arXiv:2507.20190}
\item \textbf{2025:} Explaining Ultramassive Quiescent Galaxies at 3 $<$ z $<$ 5 in the Context of Their Environments. \textit{Christian Kragh Jespersen, Adam C. Carnall, \textbf{Christopher C. Lovell}}, The Astrophysical Journal 988 L19. \href{https://arxiv.org/abs/2507.05340}{arXiv:2507.05340}
\item \textbf{2025:} First Light and Reionization Epoch Simulations (FLARES) -- XVIII: the ionising emissivities and hydrogen recombination line properties of early AGN. \textit{Stephen M. Wilkins, Aswin P. Vijayan \& others including Christopher C. Lovell}, Submitted to the Open Journal of Astrophysics. \href{https://arxiv.org/abs/2505.05257}{arXiv:2505.05257}
\item \textbf{2025:} First Light And Reionisation Epoch Simulations (FLARES): XVI. Size evolution of massive dusty galaxies at cosmic dawn from the ultraviolet to infrared. \textit{Paurush Punyasheel, Aswin P. Vijayan \& others including Christopher C. Lovell}, Astronomy and Astrophysics 696 A234. \href{https://arxiv.org/abs/2408.11037}{arXiv:2408.11037}
\item \textbf{2025:} First Light and Reionization Epoch Simulations (FLARES) - XVII. Learning the galaxy-halo connection at high redshifts. \textit{Maxwell G. A. Maltz, Peter A. Thomas, \textbf{Christoper C. Lovell} \& others}, Monthly Notices of the Royal Astronomical Society 538 3084. \href{https://arxiv.org/abs/2410.24082}{arXiv:2410.24082}
\item \textbf{2025:} First Light and Reionization Epoch Simulations (FLARES) – XV: The physical properties of super-massive black holes and their impact on galaxies in the early universe. \textit{Stephen Wilkins, Jussi K. Kuusisto \& others including Christopher C. Lovell}, The Open Journal of Astrophysics 8 29. \href{https://arxiv.org/abs/2404.02815}{arXiv:2404.02815}
\item \textbf{2025:} Euclid Quick Data Release (Q1). Extending the quest for little red dots to z$<$4. \textit{Euclid Collaboration, L. Bisigello \& others including Christopher C. Lovell}, Accepted in A\&A. \href{https://arxiv.org/abs/2503.15323}{arXiv:2503.15323}
\item \textbf{2025:} Euclid Quick Data Release (Q1). An investigation of optically faint, red objects in the Euclid Deep Fields. \textit{Euclid Collaboration, G. Girardi \& others including Christopher C. Lovell}, Paper submitted as part of the A\&A. \href{https://arxiv.org/abs/2503.15322}{arXiv:2503.15322}
\item \textbf{2025:} Euclid Quick Data Release (Q1). A probabilistic classification of quenched galaxies. \textit{Euclid Collaboration, P. Corcho-Caballero \& others including Christopher C. Lovell}, Accepted for publication in A\&A. \href{https://arxiv.org/abs/2503.15315}{arXiv:2503.15315}
\item \textbf{2025:} Euclid Quick Data Release (Q1): The evolution of the passive-density and morphology-density relations between $z=0.25$ and $z=1$. \textit{Euclid Collaboration, C. Cleland \& others including Christopher C. Lovell}, Paper submitted as part of the A\&A. \href{https://arxiv.org/abs/2503.15313}{arXiv:2503.15313}
\item \textbf{2025:} Like a candle in the wind: the embers of once aflame, now smouldering galaxies at 5 $<$ z $<$ 8. \textit{James A. A. Trussler, Christopher J. Conselice \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 537 3662. \href{https://arxiv.org/abs/2404.07163}{arXiv:2404.07163}
\item \textbf{2025:} On the Significance of Rare Objects at High Redshift: The Impact of Cosmic Variance. \textit{Christian Kragh Jespersen, Charles L. Steinhardt \& others including Christopher C. Lovell}, The Astrophysical Journal 982 23. \href{https://arxiv.org/abs/2403.00050}{arXiv:2403.00050}
\item \textbf{2025:} The Spectral Energy Distributions of Galaxies. \textit{Kartheik G. Iyer, Camilla Pacifici \& others including Christopher C. Lovell}, chapter for the Encyclopedia of Astrophysics. \href{https://arxiv.org/abs/2502.17680}{arXiv:2502.17680}
\item \textbf{2025:} Field-level simulation-based inference with galaxy catalogs: the impact of systematic effects. \textit{Natalí S. M. de Santi, Francisco Villaescusa-Navarro \& others including Christopher C. Lovell}, Journal of Cosmology and Astroparticle Physics 2025 082. \href{https://arxiv.org/abs/2310.15234}{arXiv:2310.15234}
\item \textbf{2025:} Tracing the evolutionary pathways of dust and cold gas in high-z quiescent galaxies with SIMBA. \textit{G. Lorenzon, D. Donevski \& others including Christopher C. Lovell}, Astronomy and Astrophysics 693 A118. \href{https://arxiv.org/abs/2404.10568}{arXiv:2404.10568}
\item \textbf{2025:} EPOCHS. IV. SED Modeling Assumptions and Their Impact on the Stellar Mass Function at 6.5 $\leq$ z $\leq$ 13.5 Using PEARLS and Public JWST Observations. \textit{Thomas Harvey, Christopher J. Conselice \& others including Christopher C. Lovell}, The Astrophysical Journal 978 89. \href{https://arxiv.org/abs/2403.03908}{arXiv:2403.03908}
\item \textbf{2024:} The JWST EXCELS survey: too much, too young, too fast? Ultra-massive quiescent galaxies at 3 $<$ z $<$ 5. \textit{A. C. Carnall, F. Cullen \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 534 325. \href{https://arxiv.org/abs/2405.02242}{arXiv:2405.02242}
\item \textbf{2024:} Unveiling the Distant Universe: Characterizing z $\geq$ 9 Galaxies in the First Epoch of COSMOS-Web. \textit{Maximilien Franco, Hollis B. Akins \& others including Christopher C. Lovell}, The Astrophysical Journal 973 23. \href{https://arxiv.org/abs/2308.00751}{arXiv:2308.00751}
\item \textbf{2024:} LtU-ILI: An All-in-One Framework for Implicit Inference in Astrophysics and Cosmology. \textit{Matthew Ho, Deaglan J. Bartlett \& others including Christopher C. Lovell}, The Open Journal of Astrophysics 7 54. \href{https://arxiv.org/abs/2402.05137}{arXiv:2402.05137}
\item \textbf{2024:} Efficient NIRCam Selection of Quiescent Galaxies at 3 $<$ z $<$ 6 in CEERS. \textit{Arianna S. Long, Jacqueline Antwi-Danso \& others including Christopher C. Lovell}, The Astrophysical Journal 970 68. \href{https://arxiv.org/abs/2305.04662}{arXiv:2305.04662}
\item \textbf{2024:} Atacama Large Aperture Submillimeter Telescope (AtLAST) science: Surveying the distant Universe. \textit{Eelco van Kampen, Tom Bakx \& others including Christopher C. Lovell}, Open Research Europe 4 122. \href{https://arxiv.org/abs/2403.02806}{arXiv:2403.02806}
\item \textbf{2024:} Cosmological baryon spread and impact on matter clustering in CAMELS. \textit{Matthew Gebhardt, Daniel Anglés-Alcázar \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 529 4896. \href{https://arxiv.org/abs/2307.11832}{arXiv:2307.11832}
\item \textbf{2024:} Star formation efficiency across large-scale galactic environments. \textit{Laya Ghodsi, Allison W. S. Man \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 528 4393. \href{https://arxiv.org/abs/2309.01277}{arXiv:2309.01277}
\item \textbf{2024:} Outshining by Recent Star Formation Prevents the Accurate Measurement of High-z Galaxy Stellar Masses. \textit{Desika Narayanan, Sidney Lower \& others including Christopher C. Lovell}, The Astrophysical Journal 961 73. \href{https://arxiv.org/abs/2306.10118}{arXiv:2306.10118}
\item \textbf{2024:} First Light And Reionisation Epoch Simulations (FLARES) - XII: The consequences of star-dust geometry on galaxies in the EoR. \textit{Aswin P. Vijayan, Peter A. Thomas, \textbf{Christopher C. Lovell} \& others}, Monthly Notices of the Royal Astronomical Society 527 7337. \href{https://arxiv.org/abs/2303.04177}{arXiv:2303.04177}
\item \textbf{2024:} iMaNGA: mock MaNGA galaxies based on IllustrisTNG and MaStar SSPs. - III. Stellar metallicity drivers in MaNGA and TNG50. \textit{Lorenza Nanni, Justus Neumann \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 527 6419. \href{https://arxiv.org/abs/2309.14257}{arXiv:2309.14257}
\item \textbf{2023:} Cosmic Evolution Early Release Science (CEERS) survey: The colour evolution of galaxies in the distant Universe. \textit{Stephen M. Wilkins, Jack C. Turner \& others including Christopher C. Lovell}, Submitted to MNRAS. \href{https://arxiv.org/abs/2311.08065}{arXiv:2311.08065}
\item \textbf{2023:} A Universal Equation to Predict $\Omega_{m}$ from Halo and Galaxy Catalogs. \textit{Helen Shao, Natalí S. M. de Santi \& others including Christopher C. Lovell}, The Astrophysical Journal 956 149. \href{https://arxiv.org/abs/2302.14591}{arXiv:2302.14591}
\item \textbf{2023:} The JWST Hubble Sequence: The Rest-frame Optical Evolution of Galaxy Structure at 1.5 $<$ z $<$ 6.5. \textit{Leonardo Ferreira, Christopher J. Conselice \& others including Christopher C. Lovell}, The Astrophysical Journal 955 94. \href{https://arxiv.org/abs/2210.01110}{arXiv:2210.01110}
\item \textbf{2023:} First light and reionization epoch simulations (FLARES) X III: the lyman-continuum emission of high-redshift galaxies. \textit{Louise T. C. Seeyave, Stephen M. Wilkins \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 525 2422. \href{https://arxiv.org/abs/2305.18174}{arXiv:2305.18174}
\item \textbf{2023:} Mapping circumgalactic medium observations to theory using machine learning. \textit{Sarah Appleby, Romeel Davé \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 525 1167. \href{https://arxiv.org/abs/2301.02001}{arXiv:2301.02001}
\item \textbf{2023:} Seeing sharper and deeper: JWST's first glimpse of the photometric and spectroscopic properties of galaxies in the epoch of reionization. \textit{James A. A. Trussler, Nathan J. Adams \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 523 3423. \href{https://arxiv.org/abs/2207.14265}{arXiv:2207.14265}
\item \textbf{2023:} Robust Field-level Likelihood-free Inference with Galaxies. \textit{Natalí S. M. de Santi, Helen Shao \& others including Christopher C. Lovell}, The Astrophysical Journal 952 69. \href{https://arxiv.org/abs/2302.14101}{arXiv:2302.14101}
\item \textbf{2023:} ALMACAL. XI. Over-densities as signposts for proto-clusters? A cautionary tale. \textit{Jianhang Chen, R. J. Ivison \& others including Christopher C. Lovell}, Astronomy and Astrophysics 675 L10. \href{https://arxiv.org/abs/2306.17313}{arXiv:2306.17313}
\item \textbf{2023:} MIGHTEE: deep 1.4 GHz source counts and the sky temperature contribution of star-forming galaxies and active galactic nuclei. \textit{C. L. Hale, I. H. Whittam \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 520 2668. \href{https://arxiv.org/abs/2211.05741}{arXiv:2211.05741}
\item \textbf{2023:} First light and reionization epoch simulations (FLARES) V: the redshift frontier. \textit{Stephen M. Wilkins, Aswin P. Vijayan, \textbf{Christopher C. Lovell} \& others}, Monthly Notices of the Royal Astronomical Society 519 3118. \href{https://arxiv.org/abs/2204.09431}{arXiv:2204.09431}
\item \textbf{2023:} First Light And Reionization Epoch Simulations (FLARES) VII: The star formation and metal enrichment histories of galaxies in the early Universe. \textit{Stephen M. Wilkins, Aswin P. Vijayan, \textbf{Christopher C. Lovell} \& others}, Monthly Notices of the Royal Astronomical Society 518 3935. \href{https://arxiv.org/abs/2208.00976}{arXiv:2208.00976}
\item \textbf{2023:} Unveiling the main sequence of galaxies at z $\geq$ 5 with the JWST: predictions from simulations. \textit{Jordan C. J. D'Silva, Claudia D. P. Lagos \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 518 456. \href{https://arxiv.org/abs/2208.06180}{arXiv:2208.06180}
\item \textbf{2022:} First Light and Reionisation Epoch Simulations (FLARES) - VI. The colour evolution of galaxies z = 5-15. \textit{Stephen M. Wilkins, Aswin P. Vijayan, \textbf{Christopher C. Lovell} \& others}, Monthly Notices of the Royal Astronomical Society 517 3227. \href{https://arxiv.org/abs/2207.10920}{arXiv:2207.10920}
\item \textbf{2022:} Chaotic and Clumpy Galaxy Formation in an Extremely Massive Reionization-era Halo. \textit{Justin S. Spilker, Christopher C. Hayward \& others including Christopher C. Lovell}, The Astrophysical Journal 929 L3. \href{https://arxiv.org/abs/2203.14972}{arXiv:2203.14972}
\item \textbf{2022:} First Light And Reionisation Epoch Simulations (FLARES) - III. The properties of massive dusty galaxies at cosmic dawn. \textit{Aswin P. Vijayan, Stephen M. Wilkins, \textbf{Christopher C. Lovell} \& others}, Monthly Notices of the Royal Astronomical Society 511 4999. \href{https://arxiv.org/abs/2108.00830}{arXiv:2108.00830}
\item \textbf{2022:} The BPT Diagram in Cosmological Galaxy Formation Simulations: Understanding the Physics Driving Offsets at High Redshift. \textit{Prerak Garg, Desika Narayanan \& others including Christopher C. Lovell}, The Astrophysical Journal 926 80. \href{https://arxiv.org/abs/2201.03564}{arXiv:2201.03564}
\item \textbf{2021:} The emergence of passive galaxies in the early Universe. \textit{P. Santini, M. Castellano \& others including Christopher C. Lovell}, Astronomy and Astrophysics 652 A30. \href{https://arxiv.org/abs/2011.10584}{arXiv:2011.10584}
\item \textbf{2021:} Cosmic Evolution of the $H_{2}$ Mass Density and the Epoch of Molecular Gas. \textit{T. K. Garratt, K. E. K. Coppin \& others including Christopher C. Lovell}, The Astrophysical Journal 912 62. \href{https://arxiv.org/abs/2103.08613}{arXiv:2103.08613}
\item \textbf{2021:} The Early Assembly History of the Most Massive Halo in the Reionization Era. \textit{Justin Scott Spilker, Manuel Aravena \& others including Christopher C. Lovell}, JWST Proposal. Cycle 1 1791.
\item \textbf{2021:} POWDERDAY: Dust Radiative Transfer for Galaxy Simulations. \textit{Desika Narayanan, Matthew J. Turk \& others including Christopher C. Lovell}, The Astrophysical Journal Supplement Series 252 12. \href{https://arxiv.org/abs/2006.10757}{arXiv:2006.10757}
\item \textbf{2018:} Dust-obscured star-forming galaxies in the early universe. \textit{Stephen M. Wilkins, Yu Feng \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 473 5363. \href{https://arxiv.org/abs/1710.01976}{arXiv:1710.01976}
\item \textbf{2017:} The properties of the first galaxies in the BlueTides simulation. \textit{Stephen M. Wilkins, Yu Feng \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 469 2517. \href{https://arxiv.org/abs/1704.00954}{arXiv:1704.00954}
\item \textbf{2016:} The photometric properties of galaxies in the early Universe. \textit{Stephen M. Wilkins, Yu Feng \& others including Christopher C. Lovell}, Monthly Notices of the Royal Astronomical Society 460 3170. \href{https://arxiv.org/abs/1605.05044}{arXiv:1605.05044}
\end{itemize}

% Generated by build_publication_list.py
